Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-07 manuscript/manuscript.Rmd
bit more rl

Mathematically, RL may be formulated using a discrete time *partially observable Markov decision process (POMDP)*.
This formalization is rather flexible and allows one, e.g., to account for situations where the agent may not fully observe the environment state, or where the only observations available to the agent are certain functions of the underlying state.
For the sake of clarity, we will present here only the class of POMDPs which are relevant to our work: fully observed POMDPs with trivial emission function (FMDPs for short).
An FMDP may be defined by the following data:

@@

>>>>

Mathematically, RL may be formulated using a discrete time *partially observable Markov decision process (POMDP)*.
This formalization is rather flexible and allows one, e.g., to account for situations where the agent may not fully observe the environment state, or where the only observations available to the agent are certain functions of the underlying state.
For the sake of clarity, we will present here only the class of POMDPs which are relevant to our work: *fully observable MDPs with a trivial emission function* (FMDPs for short).
An FMDP may be defined by the following data:

@@

As the name implies, the agent observes the full state of the environment of an FMDP, and chooses its next action based on this observation according to a *policy function* $\pi(a_t | s_t)$.
In return, the agent receives a discounted reward $\gamma^t r(a_t, s_t)$.
The discount factor helps regularize the agent, helping the optimization algorithm find solutions which pay off within a timescale of $t \sim \log(\gamma^{-1})$.
